Ideas cascading into keystrokes -- modelling writing hesitations as finite mixture process

### 2023-12-25 report/appendix_shift_constr.Rmd
Last draft before feedback on docs

apa_table(tmp[,-1],
          align = c("l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for key transitions immediately preceding a sentence. Cell means are shown for transitions that do and do not involve the transition to the character following shift in msecs for the slowdown for long transitions and the probability of hesitant transitions. The difference for including the transition duration to the character after shift is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95% PIs in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          font_size = "footnotesize",
          longtable = T,
          stub_indents = list("Fluent transitions" = 1,
                              "Hesitation duration" = 2:3,
                              "Hesitation probability" = 4:5) )

>>>>

apa_table(tmp[,-1],
          align = c("l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for key transitions immediately preceding a sentence. Cell means are shown for transitions that do and do not involve the transition to the character following shift in msecs for the slowdown and the probability of hesitant transitions. The difference for including the transition duration to the character after shift is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95% PIs in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          font_size = "footnotesize",
          longtable = T,
          stub_indents = list("Fluent transitions" = 1,
                              "Hesitation duration" = 2:3,
                              "Hesitation probability" = 4:5) )

### 2023-12-25 report/appendix_shift_constr.tex
Last draft before feedback on docs

\begin{longtable}{lrrrr}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:shiftcellmeans}Mixture model estimates for key transitions immediately preceding a sentence. Cell means are shown for transitions that do and do not involve the transition to the character following shift in msecs for the slowdown for long transitions and the probability of hesitant transitions. The difference for including the transition duration to the character after shift is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95\% PIs in brackets.}\\
\toprule
Language & \multicolumn{1}{c}{\_\textasciicircum{}[shift] + C} & \multicolumn{1}{c}{\_\textasciicircum{}[shift]} & \multicolumn{1}{c}{Difference} & \multicolumn{1}{c}{BF}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:shiftcellmeans} continued}}\\
\toprule
Language & \multicolumn{1}{c}{\_\textasciicircum{}[shift] + C} & \multicolumn{1}{c}{\_\textasciicircum{}[shift]} & \multicolumn{1}{c}{Difference} & \multicolumn{1}{c}{BF}\\
\midrule
\endhead
Fluent transitions &  &  &  & \\
\ \ \ overall & 156 [145, 169] & 159 [147, 172] & -0.02 [-0.13, 0.09] & 0.06\\
Hesitation duration &  &  &  & \\
\ \ \ L1 & 1,167 [1,037, 1,305] & 1,281 [1,082, 1,496] & -0.06 [-0.21, 0.09] & 0.11\\
\ \ \ L2 & 2,019 [1,772, 2,292] & 1,802 [1,557, 2,073] & 0.12 [-0.02, 0.27] & 0.29\\
Hesitation probability &  &  &  & \\
\ \ \ L1 & 1.00 [.99, 1.00] & .78 [.69, .86] & 4.91 [3.68, 6.35] & > 100\\
\ \ \ L2 & 1.00 [.99, 1.00] & .92 [.87, .96] & 3.4 [2.12, 4.85] & > 100\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

>>>>

\begin{longtable}{lrrrr}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:shiftcellmeans}Mixture model estimates for key transitions immediately preceding a sentence. Cell means are shown for transitions that do and do not involve the transition to the character following shift in msecs for the slowdown and the probability of hesitant transitions. The difference for including the transition duration to the character after shift is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95\% PIs in brackets.}\\
\toprule
Language & \multicolumn{1}{c}{\_\textasciicircum{}[shift] + C} & \multicolumn{1}{c}{\_\textasciicircum{}[shift]} & \multicolumn{1}{c}{Difference} & \multicolumn{1}{c}{BF}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:shiftcellmeans} continued}}\\
\toprule
Language & \multicolumn{1}{c}{\_\textasciicircum{}[shift] + C} & \multicolumn{1}{c}{\_\textasciicircum{}[shift]} & \multicolumn{1}{c}{Difference} & \multicolumn{1}{c}{BF}\\
\midrule
\endhead
Fluent transitions &  &  &  & \\
\ \ \ overall & 156 [145, 169] & 159 [147, 172] & -0.02 [-0.13, 0.09] & 0.06\\
Hesitation duration &  &  &  & \\
\ \ \ L1 & 1,167 [1,037, 1,305] & 1,281 [1,082, 1,496] & -0.06 [-0.21, 0.09] & 0.11\\
\ \ \ L2 & 2,019 [1,772, 2,292] & 1,802 [1,557, 2,073] & 0.12 [-0.02, 0.27] & 0.29\\
Hesitation probability &  &  &  & \\
\ \ \ L1 & 1.00 [.99, 1.00] & .78 [.69, .86] & 4.91 [3.68, 6.35] & > 100\\
\ \ \ L2 & 1.00 [.99, 1.00] & .92 [.87, .96] & 3.4 [2.12, 4.85] & > 100\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}
